`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the percentage of MRMSE
changes to discussion

\section{Discussion}\label{DiscussionSection}
This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from intracranial EEG / LFP data. The results indicate good estimation performance, where the mean parameter estimates are close to the actual values. The distributions of the estimates of the connectivity kernel parameters show a relatively wide spreads, which is expected considering the large disturbances in the system that is driven by noise. In addition the observations contain a large amount of noise.

To reduce the effect of noise, an evoked response paradigm should be considered when using real data.

The main contribution of this paper is the methodology for...

@@

The closest competitor to the integrodifference equation based approach is perhaps the multivariate auto-regressive (MVAR) model. An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres. A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain. A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper. In addition to estimating connectivity independently of the number of observations  The advantage of the methodology presented in this paper, is that

>>>>

\section{Discussion}\label{DiscussionSection}
This paper has presented an method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. The results indicate good estimation performance, where the mean parameter estimates are in accordance to the actual values. The distributions of the estimates of the connectivity kernel parameters show a relatively broad, which is expected considering the large disturbances in the system that is driven by noise. In addition the observations contain a large amount of noise.

To overcome the effect of noise, an evoked response paradigm should be considered when using real data. Following such a paradigm, data can be epoched into a sufficient number of realisations such that the a distribution of the estimates can be formed.

@@

The closest competitor to the integro-difference equation based approach is perhaps the multivariate auto-regressive (MVAR) model. An advantage of the MVAR-based methods is that they allow for anisotropic connectivity, which is present in cortico-cortical fibres. A recent theoretical study~\cite{Jirsa2009} has demonstrated the importance of this multi-scale structure in generating the characteristic rhythms of the brain. A possible method of creating more precise models with this multi-scale structure maybe to estimate anisotropic cortico-cortical connectivity using a MVAR approach and intracortical connectivity using the methods proposed in this paper. In addition to estimating connectivity independently of the number of observations, the advantage of the methodology presented in this paper, is that the number of parameters required to model the system is considerably less, and the parameter have physical meaning.
